---
title: "Activities"
author: "Isaac Amouzou"
format: html
editor: visual
---

```{r}
library(tidyverse)
```

# Activity 5

```{r}
cherry_data_selected <- read.csv("Data/cherry-bloom-early.csv") %>%
  select(early_bloom,location,matches('tmax'))
```

# Activity 6

```{r}
library(randomForest)

cherry_data_selected <-  cherry_data_selected %>% 
  mutate(early_bloom = fct_relevel(early_bloom, 'no'))

fitted_rf <- randomForest(early_bloom ~ ., data = cherry_data_selected)

```

```{r}
library(pROC)
library(randomForest)

rf_roc <- roc(response = cherry_data_selected$early_bloom,
              predictor = predict(fitted_rf, type = "prob")[, "yes"],
              levels = c("no", "yes"),
              direction = "<")

plot(rf_roc, print.auc = TRUE)
```

The randomforest method is a machine learning model that uses multiple trees - which are each trained on randomly selected subsets of the data - as an ensemble method with prediction by voting between the trees to predict a class (in this case whether or not an early bloom occurs)

The AUC-ROC method is a way to evaluate the performance of a classification model by comparing true positive rate and false positive rate . In this case with a AUC: 0.656, the model performs somewhat better than random guessing.
